\judul

### 2025-04-24 article/apendix.tex
shrink matplotlib pgf to graph size, change library name for comparison method to computational method used, add full stop to captions, add psuedocode for training, change figure placement to hbp to reduce dead whitespace.

\section{Burgers' Equation Comparison}\label{sec:burgers_comparison}
\begin{figure}[H]
  \centering
  \begin{adjustwidth}{-0.05\linewidth}{-0.05\linewidth}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_lssvr_pred_0.0.pgf}
      \end{adjustbox}
      \caption{SpectralSVR prediction.}\label{fig:comp_lssvr_pred_0.0}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_lssvr_diff_0.0.pgf}
      \end{adjustbox}
      \caption{SpectralSVR difference with target.}\label{fig:comp_lssvr_diff_0.0}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_fnn_pred_0.0.pgf}
      \end{adjustbox}
      \caption{SpectralSVR prediction.}\label{fig:comp_fnn_pred_0.0}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_fnn_diff_0.0.pgf}
      \end{adjustbox}
      \caption{SpectralSVR difference with target.}\label{fig:comp_fnn_diff_0.0}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_spo_pred_0.0.pgf}
      \end{adjustbox}
      \caption{SciPy \& NumPy prediction.}\label{fig:comp_spo_pred_0.0}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_spo_diff_0.0.pgf}
      \end{adjustbox}
      \caption{SciPy \& NumPy difference with target.}\label{fig:comp_spo_diff_0.0}
    \end{subfigure}
  \end{adjustwidth}
  \caption{Comparison of our model (SpectralSVR) and numerical methods for the Forced Burgers equation with viscosity \(\nu=0.0\).}\label{fig:comparison_burgers_0.0}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{adjustwidth}{-0.05\linewidth}{-0.05\linewidth}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_lssvr_pred_0.01.pgf}
      \end{adjustbox}
      \caption{SpectralSVR prediction.}\label{fig:comp_lssvr_pred_0.01}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_lssvr_diff_0.01.pgf}
      \end{adjustbox}
      \caption{SpectralSVR difference with target.}\label{fig:comp_lssvr_diff_0.01}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_fnn_pred_0.01.pgf}
      \end{adjustbox}
      \caption{SpectralSVR prediction.}\label{fig:comp_fnn_pred_0.01}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_fnn_diff_0.01.pgf}
      \end{adjustbox}
      \caption{SpectralSVR difference with target.}\label{fig:comp_fnn_diff_0.01}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_spo_pred_0.01.pgf}
      \end{adjustbox}
      \caption{SciPy \& NumPy prediction.}\label{fig:comp_spo_pred_0.01}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_spo_diff_0.01.pgf}
      \end{adjustbox}
      \caption{SciPy \& NumPy difference with target.}\label{fig:comp_spo_diff_0.01}
    \end{subfigure}
  \end{adjustwidth}
  \caption{Comparison of our model (SpectralSVR) and numerical methods for the Forced Burgers equation with viscosity \(\nu=0.01\).}\label{fig:comparison_burgers_0.01}
\end{figure}
\begin{table}[H]
  \caption{Metrics for predicting the exact solution for SpectralSVR (Ours) method}\label{table:comparison_exact_metrics_lssvr}
  \centering
  \begin{tabular}{lcccc}
    \toprule
    \(\nu \) & MSE  & RMSE & MAE  & sMAPE \\
    \midrule
    0.0      & 0.01 & 0.07 & 0.06 & 1.99  \\
    0.01     & 0.00 & 0.07 & 0.06 & 1.61  \\
    0.1      & 0.00 & 0.02 & 0.02 & 1.47  \\
    \bottomrule
  \end{tabular}
\end{table}
\begin{table}[H]
  \caption{Metrics for predicting the exact solution for SpectralSVR (FNN) baseline method}\label{table:comparison_exact_metrics_fnn}
  \centering
  \begin{tabular}{lcccc}
    \toprule
    \(\nu \) & MSE & RMSE & MAE & sMAPE \\
    \midrule
    0.0      & inf & inf  & inf & 1.99  \\
    0.01     & inf & inf  & inf & 1.98  \\
    0.1      & inf & inf  & inf & 1.98  \\
    \bottomrule
  \end{tabular}
\end{table}
\begin{table}[H]
  \caption{Metrics for predicting the exact solution for the lsoda method}\label{table:comparison_exact_metrics_lsoda}
  \centering
  \begin{tabular}{lcccc}
    \toprule
    \(\nu \) & MSE  & RMSE & MAE  & sMAPE \\
    \midrule
    0.0      & 0.00 & 0.00 & 0.00 & 0.00  \\
    0.01     & 0.00 & 0.00 & 0.00 & 0.08  \\
    0.1      & 0.00 & 0.04 & 0.04 & 1.52  \\
    \bottomrule
  \end{tabular}
\end{table}
\begin{table}[H]
  \caption{Metrics for predicting the exact solution for the IABM method}\label{table:comparison_exact_metrics_iabm}
  \centering
  \begin{tabular}{lcccc}
    \toprule
    \(\nu \) & MSE  & RMSE & MAE  & sMAPE \\
    \midrule
    0.0      & 0.00 & 0.00 & 0.00 & 0.00  \\
    0.01     & nan  & nan  & nan  & nan   \\
    0.1      & nan  & nan  & nan  & nan   \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\section{Burgers' Equation Comparison}\label{sec:burgers_comparison}
\begin{figure}[H]
  \centering
  \begin{adjustwidth}{-0.05\linewidth}{-0.05\linewidth}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_lssvr_pred_0.0.pgf}
      \end{adjustbox}
      \caption{SpectralSVR prediction.}\label{fig:comp_lssvr_pred_0.0}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_lssvr_diff_0.0.pgf}
      \end{adjustbox}
      \caption{SpectralSVR difference with target.}\label{fig:comp_lssvr_diff_0.0}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_fnn_pred_0.0.pgf}
      \end{adjustbox}
      \caption{SpectralSVR prediction.}\label{fig:comp_fnn_pred_0.0}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_fnn_diff_0.0.pgf}
      \end{adjustbox}
      \caption{SpectralSVR difference with target.}\label{fig:comp_fnn_diff_0.0}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_spo_pred_0.0.pgf}
      \end{adjustbox}
      \caption{lsoda prediction.}\label{fig:comp_spo_pred_0.0}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_spo_diff_0.0.pgf}
      \end{adjustbox}
      \caption{lsoda difference with target.}\label{fig:comp_spo_diff_0.0}
    \end{subfigure}
  \end{adjustwidth}
  \caption{Comparison of our model (SpectralSVR) and numerical methods for the Forced Burgers equation with viscosity \(\nu=0.0\).}\label{fig:comparison_burgers_0.0}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{adjustwidth}{-0.05\linewidth}{-0.05\linewidth}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_lssvr_pred_0.01.pgf}
      \end{adjustbox}
      \caption{SpectralSVR prediction.}\label{fig:comp_lssvr_pred_0.01}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_lssvr_diff_0.01.pgf}
      \end{adjustbox}
      \caption{SpectralSVR difference with target.}\label{fig:comp_lssvr_diff_0.01}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_fnn_pred_0.01.pgf}
      \end{adjustbox}
      \caption{SpectralSVR prediction.}\label{fig:comp_fnn_pred_0.01}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_fnn_diff_0.01.pgf}
      \end{adjustbox}
      \caption{SpectralSVR difference with target.}\label{fig:comp_fnn_diff_0.01}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_spo_pred_0.01.pgf}
      \end{adjustbox}
      \caption{lsoda prediction.}\label{fig:comp_spo_pred_0.01}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/comparisons/burgers_rollout_spo_diff_0.01.pgf}
      \end{adjustbox}
      \caption{lsoda difference with target.}\label{fig:comp_spo_diff_0.01}
    \end{subfigure}
  \end{adjustwidth}
  \caption{Comparison of our model (SpectralSVR) and numerical methods for the Forced Burgers equation with viscosity \(\nu=0.01\).}\label{fig:comparison_burgers_0.01}
\end{figure}
\begin{table}[H]
  \caption{Metrics for predicting the exact solution for SpectralSVR (Ours) method.}\label{table:comparison_exact_metrics_lssvr}
  \centering
  \begin{tabular}{lcccc}
    \toprule
    \(\nu \) & MSE  & RMSE & MAE  & sMAPE \\
    \midrule
    0.0      & 0.01 & 0.07 & 0.06 & 1.99  \\
    0.01     & 0.00 & 0.07 & 0.06 & 1.61  \\
    0.1      & 0.00 & 0.02 & 0.02 & 1.47  \\
    \bottomrule
  \end{tabular}
\end{table}
\begin{table}[H]
  \caption{Metrics for predicting the exact solution for SpectralSVR (FNN) baseline method.}\label{table:comparison_exact_metrics_fnn}
  \centering
  \begin{tabular}{lcccc}
    \toprule
    \(\nu \) & MSE & RMSE & MAE & sMAPE \\
    \midrule
    0.0      & inf & inf  & inf & 1.99  \\
    0.01     & inf & inf  & inf & 1.98  \\
    0.1      & inf & inf  & inf & 1.98  \\
    \bottomrule
  \end{tabular}
\end{table}
\begin{table}[H]
  \caption{Metrics for predicting the exact solution for the lsoda method.}\label{table:comparison_exact_metrics_lsoda}
  \centering
  \begin{tabular}{lcccc}
    \toprule
    \(\nu \) & MSE  & RMSE & MAE  & sMAPE \\
    \midrule
    0.0      & 0.00 & 0.00 & 0.00 & 0.00  \\
    0.01     & 0.00 & 0.00 & 0.00 & 0.08  \\
    0.1      & 0.00 & 0.04 & 0.04 & 1.52  \\
    \bottomrule
  \end{tabular}
\end{table}
\begin{table}[H]
  \caption{Metrics for predicting the exact solution for the IABM method.}\label{table:comparison_exact_metrics_iabm}
  \centering
  \begin{tabular}{lcccc}
    \toprule
    \(\nu \) & MSE  & RMSE & MAE  & sMAPE \\
    \midrule
    0.0      & 0.00 & 0.00 & 0.00 & 0.00  \\
    0.01     & nan  & nan  & nan  & nan   \\
    0.1      & nan  & nan  & nan  & nan   \\
    \bottomrule
  \end{tabular}
\end{table}
